---
title: Empathy Middle School Analyses with Pilot
author: Erika Weisz
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r set wd and read data, include=FALSE}
#Set working directory to the location of this .Rmd file (note: the dataset should be in the same folder)
  setwd("~/Dropbox/middleSchoolManuscript/Current")
  d0 = read.csv('empathyMiddleSchool_withPilot.csv')
```

```{r install packages, include=FALSE}
#install packages
library("knitr") 
library("plyr")
library("dplyr")
library("ggplot2")
library("gridExtra")
library("grid")
library("lattice")
library("psych")
library("lsr")
library("effsize")
library("weights")
library("ggpubr")
library("lavaan")
```

```{r knit functions, echo=FALSE}
#formatting p-values for APA
format_pval <- function(x){
  if (x < .001) return(paste('<', '.001'))
  if (x > .1) return(paste('=', rd(x, 2)))
  paste('=', rd(x, 3))   # 3 = no. of digits to round p value to if p < .001 
}
##########################################
```

```{r changing levels for figure, include=FALSE}
levels(d0$Group) 
#default is Control, Malleable, Social Norms

d0$Group <- factor(d0$Group, levels = c("CI","SNI","MMI"))
#Levels now set to Control, Social Norms, Malleable Mindset for figure
#CI = Control
#MMI = Malleable Mindset
#SNI = Social Norms
```

```{r setting school as a factor, include=FALSE}
d0$School = as.factor(d0$School) #make sure it's not is numeric
```


#Normativity Beliefs
```{r normativity beliefs, include=FALSE}
#assessing scores on beliefs about the normativity of empathy questionnaire at follow up 1
normativityAOV = aov(NormsTotal ~ Group, data=d0)
  nbG_aov = summary(normativityAOV)
  nbG_eta = etaSquared(normativityAOV)

#comparisons 
bartlett.test(NormsTotal~Group, data = d0) #don't assume equal variance

#Social Norms and Control
nbG_SNI_CI_t = t.test(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="CI"],var.equal = FALSE)
nbG_SNI_CI_d = cohen.d(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)

#Social Norms and Malleable Mindset
nbG_SNI_MMI_t = t.test(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="MMI"],var.equal = FALSE)
nbG_SNI_MMI_d = cohen.d(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="MMI"],return.dm=TRUE, na.rm=TRUE)

#Malleable Mindset and Control
nbG_MMI_CI_t = t.test(d0$NormsTotal[d0$Group=="MMI"],d0$NormsTotal[d0$Group=="CI"],var.equal = FALSE)
nbG_MMI_CI_d = cohen.d(d0$NormsTotal[d0$Group=="MMI"],d0$NormsTotal[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)

```
(Ordered by appearance in manuscript)  

#####Normativity beliefs by group [nbG]
*F*(`r nbG_aov[[1]][["Df"]][1]`, `r nbG_aov[[1]][["Df"]][2]`) = `r rd(nbG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(nbG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(nbG_eta[1],3)`

#####Social Norms and Control Norms Beliefs [nbG_SNI_CI]  
*t*(`r rd(nbG_SNI_CI_t$par,2)`) = `r rd(nbG_SNI_CI_t$stat,2)`, *p* `r format_pval(nbG_SNI_CI_t$p.value)`, 95% CI [`r rd(nbG_SNI_CI_t$conf.int[1],2)`, `r rd(nbG_SNI_CI_t$conf.int[2],2)`], *d* = `r rd(nbG_SNI_CI_d$est,2)`

#####Social Norms and Malleable Mindset Norms Beliefs [nbG_SNI_MMI]  
*t*(`r rd(nbG_SNI_MMI_t$par,2)`) = `r rd(nbG_SNI_MMI_t$stat,2)`, *p* `r format_pval(nbG_SNI_MMI_t$p.value)`, 95% CI [`r rd(nbG_SNI_MMI_t$conf.int[1],2)`, `r rd(nbG_SNI_MMI_t$conf.int[2],2)`], *d* = `r rd(nbG_SNI_MMI_d$est,2)`

#####Malleable Mindset and Control Norms Beliefs [nbG_MMI_CI]  
*t*(`r rd(nbG_MMI_CI_t$par,2)`) = `r rd(nbG_MMI_CI_t$stat,2)`, *p* `r format_pval(nbG_MMI_CI_t$p.value)`, 95% CI [`r rd(nbG_MMI_CI_t$conf.int[1],2)`, `r rd(nbG_MMI_CI_t$conf.int[2],2)`], *d* = `r rd(nbG_MMI_CI_d$est,2)`


#Malleability beliefs by group
```{r malleability beliefs, include=FALSE}
#assessing scores on beliefs about the malleability of empathy questionnaire at follow up 1
malleabilityAOV = aov(MalTotal ~ Group, data=d0)
  mbG_aov = summary(malleabilityAOV)
  mbG_eta = etaSquared(malleabilityAOV)
```
#####Malleability beliefs by group [mbG] 
*F*(`r mbG_aov[[1]][["Df"]][1]`, `r mbG_aov[[1]][["Df"]][2]`) = `r rd(mbG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(mbG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(mbG_eta[1],3)`


#Physical aggression by group
```{r physical aggression, include=FALSE}
#Comparing scores on self-reported physical aggression

physAOV = aov(CSBSphys ~ Group, data=d0)
  paG_aov = summary(physAOV)
  paG_eta = etaSquared(physAOV)
```
#####Physical aggression by group [paG] 
*F*(`r paG_aov[[1]][["Df"]][1]`, `r paG_aov[[1]][["Df"]][2]`) = `r rd(paG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(paG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(paG_eta[1],3)`


#Relational aggression by group
```{r relational aggression, include=FALSE}
#Comparing scores on self-reported relational aggression

raggAOV = aov(CSBSrelat ~ Group, data=d0)
  raG_aov = summary(raggAOV)
  raG_eta = etaSquared(raggAOV)
```
#####Relational aggression by group [raG] 
*F*(`r raG_aov[[1]][["Df"]][1]`, `r raG_aov[[1]][["Df"]][2]`) = `r rd(raG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(raG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(raG_eta[1],3)`


#Stress by group
```{r stress, include=FALSE}
#Comparing scores on self-reported stress

stressAOV = aov(PSSTotal ~ Group, data=d0)
  sG_aov = summary(stressAOV)
  sG_eta = etaSquared(stressAOV)
```
#####Stress by group [sG] 
*F*(`r sG_aov[[1]][["Df"]][1]`, `r sG_aov[[1]][["Df"]][2]`) = `r rd(sG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(sG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(sG_eta[1],3)`


#Loneliness by group
```{r loneliness, include=FALSE}
#Comparing scores on self-reported loneliness

lonelyAOV = aov(LonelyTotal ~ Group, data=d0)
  lG_aov = summary(lonelyAOV)
  lG_eta = etaSquared(lonelyAOV)
```
#####Loneliness by group [l] 
*F*(`r lG_aov[[1]][["Df"]][1]`, `r lG_aov[[1]][["Df"]][2]`) = `r rd(lG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(lG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(lG_eta[1],3)`


#Empathic concern by group
```{r empathic concern, include=FALSE}
#Comparing scores on self-reported empathic concern

ecAOV = aov(ECtotal ~ Group, data=d0)
  ecG_aov = summary(ecAOV)
  ecG_eta = etaSquared(ecAOV)
```
#####Empathic concern by group [ecG] 
*F*(`r ecG_aov[[1]][["Df"]][1]`, `r ecG_aov[[1]][["Df"]][2]`) = `r rd(ecG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(ecG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(ecG_eta[1],3)`


#Perspective taking by group
```{r perspective taking, include=FALSE}
#Comparing scores on self-reported perspective taking

ptAOV = aov(PTtotal ~ Group, data=d0)
  ptG_aov = summary(ptAOV)
  ptG_eta = etaSquared(ptAOV)
```
#####Perspective taking by group [ptG] 
*F*(`r ptG_aov[[1]][["Df"]][1]`, `r ptG_aov[[1]][["Df"]][2]`) = `r rd(ptG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(ptG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(ptG_eta[1],3)`


#Personal Distress by group
```{r personal distress, include=FALSE}
#Comparing scores on self-reported personal distress

pdAOV = aov(PDtotal ~ Group, data=d0)
  pdG_aov = summary(pdAOV)
  pdG_eta = etaSquared(pdAOV)
```
#####Personal Distress by group [pdG] 
*F*(`r pdG_aov[[1]][["Df"]][1]`, `r pdG_aov[[1]][["Df"]][2]`) = `r rd(pdG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(pdG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(pdG_eta[1],3)`


#Peer-reported prosocial behavior by group
```{r peer reported prosocial behavior, include=FALSE}
proNomsAOV = aov(prosocialNomsTotal ~ Group, data=d0)
  ppG_aov = summary(proNomsAOV)
  ppG_eta = etaSquared(proNomsAOV)
```
#####Peer-reported prosocial behavior by group [ppG] 
*F*(`r ppG_aov[[1]][["Df"]][1]`, `r ppG_aov[[1]][["Df"]][2]`) = `r rd(ppG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(ppG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(ppG_eta[1],3)`


#Self-reported prosocial behavior by group
```{r self-reported prosocial behavior, include=FALSE}
#Comparing scores on self-reported prosocial behavior

selfProAOV = aov(CSBSprosocial ~ Group, data=d0)
  spG_aov = summary(selfProAOV)
  spG_eta = etaSquared(selfProAOV)
```
#####Self-reported prosocial behavior by group [spG] 
*F*(`r spG_aov[[1]][["Df"]][1]`, `r spG_aov[[1]][["Df"]][2]`) = `r rd(spG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(spG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(spG_eta[1],3)`


#Intervention self engagement by group
```{r intervention engagement self, include=FALSE}
#assessing self-reported engagement during three intervention sessions
engageSelfAOV = aov(carefulYouSesAvg ~ Group, data=d0)
  seG_aov = summary(engageSelfAOV)
  seG_eta = etaSquared(engageSelfAOV)
```
#####Intervention self engagement by group [seG] 
*F*(`r seG_aov[[1]][["Df"]][1]`, `r seG_aov[[1]][["Df"]][2]`) = `r rd(seG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(seG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(seG_eta[1],3)`


#Intervention peer engagement by group
```{r intervention engagement peers, include=FALSE}
#assessing perceptions of peer engagement during three intervention sessions
engagePeersAOV = aov(carefulPeersSesAvg ~ Group, data=d0)
  peG_aov = summary(engagePeersAOV)
  peG_eta = etaSquared(engagePeersAOV)
```
#####Intervention peer engagement by group [peG] 
*F*(`r peG_aov[[1]][["Df"]][1]`, `r peG_aov[[1]][["Df"]][2]`) = `r rd(peG_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(peG_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(peG_eta[1],3)`


#Intervention self engagement by school
```{r intervention engagement self by school, include=FALSE}
#assessing self-reported engagement during three intervention sessions (looking across schools)
engageSelfSchoolAOV = aov(carefulYouSesAvg ~ School, data=d0)
  seS_aov = summary(engageSelfSchoolAOV)
  seS_eta = etaSquared(engageSelfSchoolAOV)

#comparisons 
bartlett.test(carefulYouSesAvg~School, data = d0) #assume equal variance

#1 and 2
seS_1_2_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = TRUE)
seS_1_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#1 and 3
seS_1_3_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="3"],var.equal = TRUE)
seS_1_3_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#1 and 4
seS_1_4_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
seS_1_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#1 and pilot
seS_1_pilot_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="pilot"],var.equal = TRUE)
seS_1_pilot_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#3 and 2
seS_3_2_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = TRUE)
seS_3_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#3 and 4
seS_3_4_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
seS_3_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#3 and pilot
seS_3_pilot_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="pilot"],var.equal = TRUE)
seS_3_pilot_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#pilot and 2
seS_pilot_2_t = t.test(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = TRUE)
seS_pilot_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#pilot and 4
seS_pilot_4_t = t.test(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
seS_pilot_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#2 and 4
seS_2_4_t = t.test(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
seS_2_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

```
#####Intervention self engagement by school [seS] 
*F*(`r seS_aov[[1]][["Df"]][1]`, `r seS_aov[[1]][["Df"]][2]`) = `r rd(seS_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(seS_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(seS_eta[1],3)`

#####1 and 2 [seS_1_2]  
*t*(`r rd(seS_1_2_t$par,2)`) = `r rd(seS_1_2_t$stat,2)`, *p* `r format_pval(seS_1_2_t$p.value)`, 95% CI [`r rd(seS_1_2_t$conf.int[1],2)`, `r rd(seS_1_2_t$conf.int[2],2)`], *d* = `r rd(seS_1_2_d$est,2)`

#####1 and 3 [seS_1_3]  
*t*(`r rd(seS_1_3_t$par,2)`) = `r rd(seS_1_3_t$stat,2)`, *p* `r format_pval(seS_1_3_t$p.value)`, 95% CI [`r rd(seS_1_3_t$conf.int[1],2)`, `r rd(seS_1_3_t$conf.int[2],2)`], *d* = `r rd(seS_1_3_d$est,2)`

#####1 and 4 [seS_1_4]  
*t*(`r rd(seS_1_4_t$par,2)`) = `r rd(seS_1_4_t$stat,2)`, *p* `r format_pval(seS_1_4_t$p.value)`, 95% CI [`r rd(seS_1_4_t$conf.int[1],2)`, `r rd(seS_1_4_t$conf.int[2],2)`], *d* = `r rd(seS_1_4_d$est,2)`

#####1 and pilot [seS_1_pilot]  
*t*(`r rd(seS_1_pilot_t$par,2)`) = `r rd(seS_1_pilot_t$stat,2)`, *p* `r format_pval(seS_1_pilot_t$p.value)`, 95% CI [`r rd(seS_1_pilot_t$conf.int[1],2)`, `r rd(seS_1_pilot_t$conf.int[2],2)`], *d* = `r rd(seS_1_pilot_d$est,2)`

#####3 and 2 [seS_3_2]  
*t*(`r rd(seS_3_2_t$par,2)`) = `r rd(seS_3_2_t$stat,2)`, *p* `r format_pval(seS_3_2_t$p.value)`, 95% CI [`r rd(seS_3_2_t$conf.int[1],2)`, `r rd(seS_3_2_t$conf.int[2],2)`], *d* = `r rd(seS_3_2_d$est,2)`

#####3 and 4 [seS_3_4]  
*t*(`r rd(seS_3_4_t$par,2)`) = `r rd(seS_3_4_t$stat,2)`, *p* `r format_pval(seS_3_4_t$p.value)`, 95% CI [`r rd(seS_3_4_t$conf.int[1],2)`, `r rd(seS_3_4_t$conf.int[2],2)`], *d* = `r rd(seS_3_4_d$est,2)`


#####3 and pilot [seS_3_pilot]  
*t*(`r rd(seS_3_pilot_t$par,2)`) = `r rd(seS_3_pilot_t$stat,2)`, *p* `r format_pval(seS_3_pilot_t$p.value)`, 95% CI [`r rd(seS_3_pilot_t$conf.int[1],2)`, `r rd(seS_3_pilot_t$conf.int[2],2)`], *d* = `r rd(seS_3_pilot_d$est,2)`

#####pilot and 2 [seS_pilot_2]  
*t*(`r rd(seS_pilot_2_t$par,2)`) = `r rd(seS_pilot_2_t$stat,2)`, *p* `r format_pval(seS_pilot_2_t$p.value)`, 95% CI [`r rd(seS_pilot_2_t$conf.int[1],2)`, `r rd(seS_pilot_2_t$conf.int[2],2)`], *d* = `r rd(seS_pilot_2_d$est,2)`

#####pilot and 4 [seS_pilot_4]  
*t*(`r rd(seS_pilot_4_t$par,2)`) = `r rd(seS_pilot_4_t$stat,2)`, *p* `r format_pval(seS_pilot_4_t$p.value)`, 95% CI [`r rd(seS_pilot_4_t$conf.int[1],2)`, `r rd(seS_pilot_4_t$conf.int[2],2)`], *d* = `r rd(seS_pilot_4_d$est,2)`

#####2 and 4 [seS_2_4]  
*t*(`r rd(seS_2_4_t$par,2)`) = `r rd(seS_2_4_t$stat,2)`, *p* `r format_pval(seS_2_4_t$p.value)`, 95% CI [`r rd(seS_2_4_t$conf.int[1],2)`, `r rd(seS_2_4_t$conf.int[2],2)`], *d* = `r rd(seS_2_4_d$est,2)`


#Intervention peer engagement by school
```{r intervention engagement peers by school, include=FALSE}
#assessing perceptions of peer engagement during three intervention sessions (looking across schools)
engagePeersSchoolAOV = aov(carefulPeersSesAvg ~ School, data=d0)
  peS_aov = summary(engagePeersSchoolAOV)
  peS_eta = etaSquared(engagePeersSchoolAOV)

#comparisons 
bartlett.test(carefulPeersSesAvg~School, data = d0) #can't assume equal variance


#1 and 2
peS_1_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = TRUE)
peS_1_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#1 and 3
peS_1_3_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="3"],var.equal = TRUE)
peS_1_3_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#1 and 4
peS_1_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
peS_1_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#1 and pilot
peS_1_pilot_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="pilot"],var.equal = TRUE)
peS_1_pilot_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#3 and 2
peS_3_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = TRUE)
peS_3_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#3 and 4
peS_3_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
peS_3_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#3 and pilot
peS_3_pilot_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="pilot"],var.equal = TRUE)
peS_3_pilot_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#pilot and 2
peS_pilot_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = TRUE)
peS_pilot_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#pilot and 4
peS_pilot_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
peS_pilot_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#2 and 4
peS_2_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
peS_2_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

```
#####Intervention peer engagement by school [peS] 
*F*(`r peS_aov[[1]][["Df"]][1]`, `r peS_aov[[1]][["Df"]][2]`) = `r rd(peS_aov[[1]][["F value"]][1],2)`, *p* `r format_pval(peS_aov[[1]][["Pr(>F)"]][1])`, $\eta$^2^  = `r rd(peS_eta[1],3)`

#####1 and 2 [peS_1_2]  
*t*(`r rd(peS_1_2_t$par,2)`) = `r rd(peS_1_2_t$stat,2)`, *p* `r format_pval(peS_1_2_t$p.value)`, 95% CI [`r rd(peS_1_2_t$conf.int[1],2)`, `r rd(peS_1_2_t$conf.int[2],2)`], *d* = `r rd(peS_1_2_d$est,2)`

#####1 and 3 [peS_1_3]  
*t*(`r rd(peS_1_3_t$par,2)`) = `r rd(peS_1_3_t$stat,2)`, *p* `r format_pval(peS_1_3_t$p.value)`, 95% CI [`r rd(peS_1_3_t$conf.int[1],2)`, `r rd(peS_1_3_t$conf.int[2],2)`], *d* = `r rd(peS_1_3_d$est,2)`

#####1 and 4 [peS_1_4]  
*t*(`r rd(peS_1_4_t$par,2)`) = `r rd(peS_1_4_t$stat,2)`, *p* `r format_pval(peS_1_4_t$p.value)`, 95% CI [`r rd(peS_1_4_t$conf.int[1],2)`, `r rd(peS_1_4_t$conf.int[2],2)`], *d* = `r rd(peS_1_4_d$est,2)`

#####1 and pilot [peS_1_pilot]  
*t*(`r rd(peS_1_pilot_t$par,2)`) = `r rd(peS_1_pilot_t$stat,2)`, *p* `r format_pval(peS_1_pilot_t$p.value)`, 95% CI [`r rd(peS_1_pilot_t$conf.int[1],2)`, `r rd(peS_1_pilot_t$conf.int[2],2)`], *d* = `r rd(peS_1_pilot_d$est,2)`

#####3 and 2 [peS_3_2]  
*t*(`r rd(peS_3_2_t$par,2)`) = `r rd(peS_3_2_t$stat,2)`, *p* `r format_pval(peS_3_2_t$p.value)`, 95% CI [`r rd(peS_3_2_t$conf.int[1],2)`, `r rd(peS_3_2_t$conf.int[2],2)`], *d* = `r rd(peS_3_2_d$est,2)`

#####3 and 4 [peS_3_4]  
*t*(`r rd(peS_3_4_t$par,2)`) = `r rd(peS_3_4_t$stat,2)`, *p* `r format_pval(peS_3_4_t$p.value)`, 95% CI [`r rd(peS_3_4_t$conf.int[1],2)`, `r rd(peS_3_4_t$conf.int[2],2)`], *d* = `r rd(peS_3_4_d$est,2)`


#####3 and pilot [peS_3_pilot]  
*t*(`r rd(peS_3_pilot_t$par,2)`) = `r rd(peS_3_pilot_t$stat,2)`, *p* `r format_pval(peS_3_pilot_t$p.value)`, 95% CI [`r rd(peS_3_pilot_t$conf.int[1],2)`, `r rd(peS_3_pilot_t$conf.int[2],2)`], *d* = `r rd(peS_3_pilot_d$est,2)`

#####pilot and 2 [peS_pilot_2]  
*t*(`r rd(peS_pilot_2_t$par,2)`) = `r rd(peS_pilot_2_t$stat,2)`, *p* `r format_pval(peS_pilot_2_t$p.value)`, 95% CI [`r rd(peS_pilot_2_t$conf.int[1],2)`, `r rd(peS_pilot_2_t$conf.int[2],2)`], *d* = `r rd(peS_pilot_2_d$est,2)`

#####pilot and 4 [peS_pilot_4]  
*t*(`r rd(peS_pilot_4_t$par,2)`) = `r rd(peS_pilot_4_t$stat,2)`, *p* `r format_pval(peS_pilot_4_t$p.value)`, 95% CI [`r rd(peS_pilot_4_t$conf.int[1],2)`, `r rd(peS_pilot_4_t$conf.int[2],2)`], *d* = `r rd(peS_pilot_4_d$est,2)`

#####2 and 4 [peS_2_4]  
*t*(`r rd(peS_2_4_t$par,2)`) = `r rd(peS_2_4_t$stat,2)`, *p* `r format_pval(peS_2_4_t$p.value)`, 95% CI [`r rd(peS_2_4_t$conf.int[1],2)`, `r rd(peS_2_4_t$conf.int[2],2)`], *d* = `r rd(peS_2_4_d$est,2)`




