---
title: Empathy Middle School Analyses
author: Erika Weisz
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r set wd and read data, include=FALSE}
#Set working directory to the location of this .Rmd file (note: the dataset should be in the same folder)
  setwd("~/Dropbox/middleSchoolManuscript/Current")
  d0 = read.csv('empathyMiddleSchool.csv')
```

```{r install packages, include=FALSE}
#install packages
library("knitr") 
library("tidyverse")
library("psych")
library("lsr")
library("effsize")
library("weights")
library("ggpubr")
library("lavaan")
```

```{r knit functions, echo=FALSE}
#formatting p-values for APA
format_pval <- function(x){
  if (x < .001) return(paste('<', '.001'))
  if (x > .1) return(paste('=', rd(x, 2)))
  paste('=', rd(x, 3))   # 3 = no. of digits to round p value to if p < .001 
}
##########################################
```

```{r changing levels for figure, include=FALSE}
levels(d0$Group) 
#default is Control, Malleable, Social Norms

d0$Group <- factor(d0$Group, levels = c("CI","SNI","MMI"))
#Levels now set to Control, Social Norms, Malleable Mindset for figure
#CI = Control
#MMI = Malleable Mindset
#SNI = Social Norms
```

```{r setting school as a factor}
#make sure school is not is numeric
d0$School = as.factor(d0$School) 
```


#Normativity beliefs by group
```{r normativity beliefs, include=FALSE}
#assessing scores on beliefs about the normativity of empathy questionnaire at follow up 1
normativityAOV = aov(NormsTotal ~ Group, data=d0)
summary(normativityAOV)
etaSquared(normativityAOV)

#comparisons 
bartlett.test(NormsTotal~Group, data = d0) #don't assume equal variance

#Social Norms and Control
nb_SNI_CI_t = t.test(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="CI"],var.equal = FALSE)
nb_SNI_CI_d = cohen.d(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)

#Social Norms and Malleable Mindset
nb_SNI_MMI_t = t.test(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="MMI"],var.equal = FALSE)
nb_SNI_MMI_d = cohen.d(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="MMI"],return.dm=TRUE, na.rm=TRUE)

#Malleable Mindset and Control
nb_MMI_CI_t = t.test(d0$NormsTotal[d0$Group=="MMI"],d0$NormsTotal[d0$Group=="CI"],var.equal = FALSE)
nb_MMI_CI_d = cohen.d(d0$NormsTotal[d0$Group=="MMI"],d0$NormsTotal[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)


```
(Ordered by appearance in manuscript)

#####Social Norms and Control Norms Beliefs [nb_SNI_CI]  
*t*(`r rd(nb_SNI_CI_t$par,2)`) = `r rd(nb_SNI_CI_t$stat,2)`, *p* `r format_pval(nb_SNI_CI_t$p.value)`, 95% CI [`r rd(nb_SNI_CI_t$conf.int[1],2)`, `r rd(nb_SNI_CI_t$conf.int[2],2)`], *d* = `r rd(nb_SNI_CI_d$est,2)`

#####Social Norms and Malleable Mindset Norms Beliefs [nb_SNI_MMI]  
*t*(`r rd(nb_SNI_MMI_t$par,2)`) = `r rd(nb_SNI_MMI_t$stat,2)`, *p* `r format_pval(nb_SNI_MMI_t$p.value)`, 95% CI [`r rd(nb_SNI_MMI_t$conf.int[1],2)`, `r rd(nb_SNI_MMI_t$conf.int[2],2)`], *d* = `r rd(nb_SNI_MMI_d$est,2)`

#####Malleable Mindset and Control Norms Beliefs [nb_MMI_CI]  
*t*(`r rd(nb_MMI_CI_t$par,2)`) = `r rd(nb_MMI_CI_t$stat,2)`, *p* `r format_pval(nb_MMI_CI_t$p.value)`, 95% CI [`r rd(nb_MMI_CI_t$conf.int[1],2)`, `r rd(nb_MMI_CI_t$conf.int[2],2)`], *d* = `r rd(nb_MMI_CI_d$est,2)`


#Malleability beliefs by group
```{r malleability beliefs, include=FALSE}
#assessing scores on beliefs about the malleability of empathy questionnaire at follow up 1
malleabilityAOV = aov(MalTotal ~ Group, data=d0)
summary(malleabilityAOV)
etaSquared(malleabilityAOV)
```

#Empathic Motives by group
```{r empathic motives, include=FALSE}
#assessing composite scores on empathic motives questionnaire at the end of the third session 
empMotivesAOV = aov(EmpMotivesComp ~ Group, data=d0)
summary(empMotivesAOV)
etaSquared(empMotivesAOV)

#comparisons 
bartlett.test(EmpMotivesComp~Group, data = d0) #assume equal variance

#Social Norms and Control
em_SNI_CI_t = t.test(d0$EmpMotivesComp[d0$Group=="SNI"],d0$EmpMotivesComp[d0$Group=="CI"],var.equal = TRUE)
em_SNI_CI_d = cohen.d(d0$EmpMotivesComp[d0$Group=="SNI"],d0$EmpMotivesComp[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)

#Social Norms and Malleable Mindset
em_SNI_MMI_t = t.test(d0$EmpMotivesComp[d0$Group=="SNI"],d0$EmpMotivesComp[d0$Group=="MMI"],var.equal = TRUE)
em_SNI_MMI_d = cohen.d(d0$EmpMotivesComp[d0$Group=="SNI"],d0$EmpMotivesComp[d0$Group=="MMI"],return.dm=TRUE, na.rm=TRUE)

#Malleable Mindset and Control
em_MMI_CI_t = t.test(d0$EmpMotivesComp[d0$Group=="MMI"],d0$EmpMotivesComp[d0$Group=="CI"],var.equal = TRUE)
em_MMI_CI_d = cohen.d(d0$EmpMotivesComp[d0$Group=="MMI"],d0$EmpMotivesComp[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)
```
(Ordered by appearance in manuscript)

#####Social and Control Empathic Motivation [em_SNI_CI]  
*t*(`r rd(em_SNI_CI_t$par,2)`) = `r rd(em_SNI_CI_t$stat,2)`, *p* `r format_pval(em_SNI_CI_t$p.value)`, 95% CI [`r rd(em_SNI_CI_t$conf.int[1],2)`, `r rd(em_SNI_CI_t$conf.int[2],2)`], *d* = `r rd(em_SNI_CI_d$est,2)`

#####Social Norms and Malleable Mindset Empathic Motivation [em_SNI_MMI]  
*t*(`r rd(em_SNI_MMI_t$par,2)`) = `r rd(em_SNI_MMI_t$stat,2)`, *p* `r format_pval(em_SNI_MMI_t$p.value)`, 95% CI [`r rd(em_SNI_MMI_t$conf.int[1],2)`, `r rd(em_SNI_MMI_t$conf.int[2],2)`], *d* = `r rd(em_SNI_MMI_d$est,2)`

#####Malleable Mindset and Control Empathic Motivation [em_MMI_CI]  
*t*(`r rd(em_MMI_CI_t$par,2)`) = `r rd(em_MMI_CI_t$stat,2)`, *p* `r format_pval(em_MMI_CI_t$p.value)`, 95% CI [`r rd(em_MMI_CI_t$conf.int[1],2)`, `r rd(em_MMI_CI_t$conf.int[2],2)`], *d* = `r rd(em_MMI_CI_d$est,2)`




#Indirect effects of group assignment on peer-reported prosocial behavior
```{r examining indirect effects of empathic motives and peer-reported prosocial behavior, warning=FALSE}
d3 = subset(d0,School != 1) #exclude school 1 school, where there wasn't a difference in empathic motives or social normativty between conditions

d3_SNI_CI = subset(d3,Group != "MMI") #remove malleable so as to compare social norms to control condition
d3_SNI_CI$Group <- factor(d3_SNI_CI$Group, levels = c("CI","SNI")) 
contrasts(d3_SNI_CI$Group)

x = d3_SNI_CI$Group
y = d3_SNI_CI$prosocialNomsTotal
m = d3_SNI_CI$EmpMotivesComp
DataProNoms <- data.frame(X = x, Y = y, M = m)

model_simplemed <-  '# direct effect
                     Y ~ c*X
                     # mediator
                     M ~ a*X
                     Y ~ b*M
                     # indirect effect (a*b)
                     ab := a*b
                     # total effect
                     total := c + (a*b)
                     '
         
fit <- sem(model_simplemed, data = DataProNoms)
summary(fit)

set.seed(1234)

#for boot strapped 95% CIs
fit <- sem(model_simplemed, data=DataProNoms, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)

boot.fit <- parameterEstimates(fit)
boot.fit
```



#Indirect effects of group assignment on loneliness
```{r examining indirect effects of empathic motives and loneliness, warning=FALSE}
d3 = subset(d0,School != 1) #exclude school 1 school, where there wasn't a difference in empathic motives or social normativty between conditions

d3_SNI_CI = subset(d3,Group != "MMI") #remove malleable so as to compare social norms to control condition
d3_SNI_CI$Group <- factor(d3_SNI_CI$Group, levels = c("CI","SNI")) 
contrasts(d3_SNI_CI$Group)

x = d3_SNI_CI$Group
y = d3_SNI_CI$LonelyTotal
m = d3_SNI_CI$EmpMotivesComp

DataLonely <- data.frame(X = x, Y = y, M = m)

model_simplemed <-  '# direct effect
                     Y ~ c*X
                     # mediator
                     M ~ a*X
                     Y ~ b*M
                     # indirect effect (a*b)
                     ab := a*b
                     # total effect
                     total := c + (a*b)
                     '
set.seed(1234)
         
fit <- sem(model_simplemed, data = DataLonely)
summary(fit)


#for boot strapped 95% CIs
fit <- sem(model_simplemed, data=DataLonely, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)

boot.fit <- parameterEstimates(fit)
boot.fit
```


#Indirect effects of group assignment on physical aggression
```{r examining indirect effects of empathic motives and physical aggression,  warning=FALSE}
d3 = subset(d0,School != 1) #exclude school 1 school, where there wasn't a difference in empathic motives or social normativty between conditions

d3_SNI_CI = subset(d3,Group != "MMI") #remove malleable so as to compare social norms to control condition
d3_SNI_CI$Group <- factor(d3_SNI_CI$Group, levels = c("CI","SNI")) 
contrasts(d3_SNI_CI$Group)

x = d3_SNI_CI$Group
y = d3_SNI_CI$CSBSphys
m = d3_SNI_CI$EmpMotivesComp

DataPhys <- data.frame(X = x, Y = y, M = m)

model_simplemed <-  '# direct effect
                     Y ~ c*X
                     # mediator
                     M ~ a*X
                     Y ~ b*M
                     # indirect effect (a*b)
                     ab := a*b
                     # total effect
                     total := c + (a*b)
                     '
set.seed(1234)         

fit <- sem(model_simplemed, data = DataPhys)
summary(fit)


#for boot strapped 95% CIs
fit <- sem(model_simplemed, data=DataPhys, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)

boot.fit <- parameterEstimates(fit)
boot.fit
```


#Indirect effects of group assignment on relational aggression
```{r examining indirect effects of empathic motives and relational aggression,  warning=FALSE}
d3 = subset(d0,School != 1) #exclude school 1 school, where there wasn't a difference in empathic motives or social normativty between conditions

d3_SNI_CI = subset(d3,Group != "MMI") #remove malleable so as to compare social norms to control condition
d3_SNI_CI$Group <- factor(d3_SNI_CI$Group, levels = c("CI","SNI")) 
contrasts(d3_SNI_CI$Group)

x = d3_SNI_CI$Group
y = d3_SNI_CI$CSBSrelat
m = d3_SNI_CI$EmpMotivesComp

DataRelat <- data.frame(X = x, Y = y, M = m)

model_simplemed <-  '# direct effect
                     Y ~ c*X
                     # mediator
                     M ~ a*X
                     Y ~ b*M
                     # indirect effect (a*b)
                     ab := a*b
                     # total effect
                     total := c + (a*b)
                     '
set.seed(1234)         

fit <- sem(model_simplemed, data = DataRelat)
summary(fit)


#for boot strapped 95% CIs
fit <- sem(model_simplemed, data=DataRelat, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)

boot.fit <- parameterEstimates(fit)
boot.fit
```


#Physical aggression by group
```{r physical aggression, include=FALSE}
#Comparing scores on self-reported physical aggression

physAOV = aov(CSBSphys ~ Group, data=d0)
summary(physAOV)
etaSquared(physAOV)
```

#Relational aggression by group
```{r relational aggression, include=FALSE}
#Comparing scores on self-reported relational aggression

raggAOV = aov(CSBSrelat ~ Group, data=d0)
summary(raggAOV)
etaSquared(raggAOV)
```

#Self-reported prosocial behavior by group
```{r self-reported prosocial behavior, include=FALSE}
#Comparing scores on self-reported prosocial behavior

selfProAOV = aov(CSBSprosocial ~ Group, data=d0)
summary(selfProAOV)
etaSquared(selfProAOV)
```

#Peer-reported prosocial behavior by group
```{r peer reported prosocial beahvior}
proNomsAOV = aov(prosocialNomsTotal ~ Group, data=d0)
summary(proNomsAOV)
etaSquared(proNomsAOV)
```

#Empathic concern by group
```{r empathic concern, include=FALSE}
#Comparing scores on self-reported empathic concern

ecAOV = aov(ECtotal ~ Group, data=d0)
summary(ecAOV)
etaSquared(ecAOV)
```

#Perspective taking by group
```{r perspective taking, include=FALSE}
#Comparing scores on self-reported perspective taking

ptAOV = aov(PTtotal ~ Group, data=d0)
summary(ptAOV)
etaSquared(ptAOV)
```

#Stress
```{r stress, include=FALSE}
#Comparing scores on self-reported stress

stressAOV = aov(PSSTotal ~ Group, data=d0)
summary(stressAOV)
etaSquared(stressAOV)
```

#Loneliness
```{r loneliness, include=FALSE}
#Comparing scores on self-reported loneliness

lonelyAOV = aov(LonelyTotal ~ Group, data=d0)
summary(lonelyAOV)
etaSquared(lonelyAOV)
```

#Personal Distress
```{r personal distress, include=FALSE}
#Comparing scores on self-reported personal distress

pdAOV = aov(PDtotal ~ Group, data=d0)
summary(pdAOV)
etaSquared(pdAOV)
```


#Intervention self engagement by school
```{r intervention engagement self by school, include=FALSE}
#assessing self-reported engagement during three intervention sessions (looking across schools)
engageSelfSchoolAOV = aov(carefulYouSesAvg ~ School, data=d0)
summary(engageSelfSchoolAOV)
etaSquared(engageSelfSchoolAOV)

#comparisons 
bartlett.test(carefulYouSesAvg~School, data = d0) #assume equal variance

#School 1 and 2
se_1_2_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = FALSE)
se_1_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 3
se_1_3_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="3"],var.equal = FALSE)
se_1_3_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 4
se_1_4_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = FALSE)
se_1_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 3
se_2_3_t = t.test(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="3"],var.equal = FALSE)
se_2_3_d = cohen.d(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 4
se_2_4_t = t.test(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = FALSE)
se_2_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 3 and 4
se_3_4_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = FALSE)
se_3_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)
```
#####Schools 2 and 4 self engagement [se_2_4]  
*t*(`r rd(se_2_4_t$par,2)`) = `r rd(se_2_4_t$stat,2)`, *p* `r format_pval(se_2_4_t$p.value)`, 95% CI [`r rd(se_2_4_t$conf.int[1],2)`, `r rd(se_2_4_t$conf.int[2],2)`], *d* = `r rd(se_2_4_d$est,2)`


#Intervention peer engagement by school
```{r intervention engagement peers by school, include=FALSE}
#assessing perceptions of peer engagement during three intervention sessions (looking across schools)
engagePeersSchoolAOV = aov(carefulPeersSesAvg ~ School, data=d0)
summary(engagePeersSchoolAOV)
etaSquared(engagePeersSchoolAOV)

#comparisons 
bartlett.test(carefulPeersSesAvg~School, data = d0) #can't assume equal variance


#School 1 and 2
pe_1_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = FALSE)
pe_1_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 3
pe_1_3_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="3"],var.equal = FALSE)
pe_1_3_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 4
pe_1_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = FALSE)
pe_1_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 3
pe_2_3_t = t.test(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="3"],var.equal = FALSE)
pe_2_3_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 4
pe_2_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = FALSE)
pe_2_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 3 and 4
pe_3_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = FALSE)
pe_3_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)
```
#####Schools 2 and 4 [pe_2_4]  
*t*(`r rd(pe_2_4_t$par,2)`) = `r rd(pe_2_4_t$stat,2)`, *p* `r format_pval(pe_2_4_t$p.value)`, 95% CI [`r rd(pe_2_4_t$conf.int[1],2)`, `r rd(pe_2_4_t$conf.int[2],2)`], *d* = `r rd(pe_2_4_d$est,2)`



#Physical Agggression by school
```{r physical aggression by school, include=FALSE}
physSchoolAOV = aov(CSBSphys ~ School, data=d0)
summary(physSchoolAOV)
etaSquared(physSchoolAOV)

#comparisons 
bartlett.test(CSBSphys~School, data = d0) #can't assume equal variance


#School 1 and 2
pa_1_2_t = t.test(d0$CSBSphys[d0$School=="1"],d0$CSBSphys[d0$School=="2"],var.equal = FALSE)
pa_1_2_d = cohen.d(d0$CSBSphys[d0$School=="1"],d0$CSBSphys[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 3
pa_1_3_t = t.test(d0$CSBSphys[d0$School=="1"],d0$CSBSphys[d0$School=="3"],var.equal = FALSE)
pa_1_3_d = cohen.d(d0$CSBSphys[d0$School=="1"],d0$CSBSphys[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 4
pa_1_4_t = t.test(d0$CSBSphys[d0$School=="1"],d0$CSBSphys[d0$School=="4"],var.equal = FALSE)
pa_1_4_d = cohen.d(d0$CSBSphys[d0$School=="1"],d0$CSBSphys[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 3
pa_2_3_t = t.test(d0$CSBSphys[d0$School=="2"],d0$CSBSphys[d0$School=="3"],var.equal = FALSE)
pa_2_3_d = cohen.d(d0$CSBSphys[d0$School=="2"],d0$CSBSphys[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 4 and 2
pa_4_2_t = t.test(d0$CSBSphys[d0$School=="4"],d0$CSBSphys[d0$School=="2"],var.equal = FALSE)
pa_4_2_d = cohen.d(d0$CSBSphys[d0$School=="4"],d0$CSBSphys[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 4 and 3
pa_4_3_t = t.test(d0$CSBSphys[d0$School=="4"],d0$CSBSphys[d0$School=="3"],var.equal = FALSE)
pa_4_3_d = cohen.d(d0$CSBSphys[d0$School=="4"],d0$CSBSphys[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)
```
#####Schools 1 and 2 [pa_1_2]  
*t*(`r rd(pa_1_2_t$par,2)`) = `r rd(pa_1_2_t$stat,2)`, *p* `r format_pval(pa_1_2_t$p.value)`, 95% CI [`r rd(pa_1_2_t$conf.int[1],2)`, `r rd(pa_1_2_t$conf.int[2],2)`], *d* = `r rd(pa_1_2_d$est,2)`

#####Schools 1 and 3 [pa_1_3]  
*t*(`r rd(pa_1_3_t$par,2)`) = `r rd(pa_1_3_t$stat,2)`, *p* `r format_pval(pa_1_3_t$p.value)`, 95% CI [`r rd(pa_1_3_t$conf.int[1],2)`, `r rd(pa_1_3_t$conf.int[2],2)`], *d* = `r rd(pa_1_3_d$est,2)`

#####Schools 1 and 4 [pa_1_4]  
*t*(`r rd(pa_1_4_t$par,2)`) = `r rd(pa_1_4_t$stat,2)`, *p* `r format_pval(pa_1_4_t$p.value)`, 95% CI [`r rd(pa_1_4_t$conf.int[1],2)`, `r rd(pa_1_4_t$conf.int[2],2)`], *d* = `r rd(pa_1_4_d$est,2)`

#####Schools 4 and 2 [pa_4_2]  
*t*(`r rd(pa_4_2_t$par,2)`) = `r rd(pa_4_2_t$stat,2)`, *p* `r format_pval(pa_4_2_t$p.value)`, 95% CI [`r rd(pa_4_2_t$conf.int[1],2)`, `r rd(pa_4_2_t$conf.int[2],2)`], *d* = `r rd(pa_4_2_d$est,2)`

#####Schools 4 and 3 [pa_4_3]  
*t*(`r rd(pa_4_3_t$par,2)`) = `r rd(pa_4_3_t$stat,2)`, *p* `r format_pval(pa_4_3_t$p.value)`, 95% CI [`r rd(pa_4_3_t$conf.int[1],2)`, `r rd(pa_4_3_t$conf.int[2],2)`], *d* = `r rd(pa_4_3_d$est,2)`


#Relational Agggression by school
```{r relational aggression by school, include=FALSE}
relatSchoolAOV = aov(CSBSrelat ~ School, data=d0)
summary(relatSchoolAOV)
etaSquared(relatSchoolAOV)

#comparisons 
bartlett.test(CSBSrelat~School, data = d0) #can't assume equal variance


#School 1 and 2
ra_1_2_t = t.test(d0$CSBSrelat[d0$School=="1"],d0$CSBSrelat[d0$School=="2"],var.equal = FALSE)
ra_1_2_d = cohen.d(d0$CSBSrelat[d0$School=="1"],d0$CSBSrelat[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 3
ra_1_3_t = t.test(d0$CSBSrelat[d0$School=="1"],d0$CSBSrelat[d0$School=="3"],var.equal = FALSE)
ra_1_3_d = cohen.d(d0$CSBSrelat[d0$School=="1"],d0$CSBSrelat[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 4
ra_1_4_t = t.test(d0$CSBSrelat[d0$School=="1"],d0$CSBSrelat[d0$School=="4"],var.equal = FALSE)
ra_1_4_d = cohen.d(d0$CSBSrelat[d0$School=="1"],d0$CSBSrelat[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 3
ra_2_3_t = t.test(d0$CSBSrelat[d0$School=="2"],d0$CSBSrelat[d0$School=="3"],var.equal = FALSE)
ra_2_3_d = cohen.d(d0$CSBSrelat[d0$School=="2"],d0$CSBSrelat[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 4 and 2
ra_4_2_t = t.test(d0$CSBSrelat[d0$School=="4"],d0$CSBSrelat[d0$School=="2"],var.equal = FALSE)
ra_4_2_d = cohen.d(d0$CSBSrelat[d0$School=="4"],d0$CSBSrelat[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 4 and 3
ra_4_3_t = t.test(d0$CSBSrelat[d0$School=="4"],d0$CSBSrelat[d0$School=="3"],var.equal = FALSE)
ra_4_3_d = cohen.d(d0$CSBSrelat[d0$School=="4"],d0$CSBSrelat[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)
```
#####Schools 1 and 2 [ra_1_2]  
*t*(`r rd(ra_1_2_t$par,2)`) = `r rd(ra_1_2_t$stat,2)`, *p* `r format_pval(ra_1_2_t$p.value)`, 95% CI [`r rd(ra_1_2_t$conf.int[1],2)`, `r rd(ra_1_2_t$conf.int[2],2)`], *d* = `r rd(ra_1_2_d$est,2)`

#####Schools 1 and 3 [ra_1_3]  
*t*(`r rd(ra_1_3_t$par,2)`) = `r rd(ra_1_3_t$stat,2)`, *p* `r format_pval(ra_1_3_t$p.value)`, 95% CI [`r rd(ra_1_3_t$conf.int[1],2)`, `r rd(ra_1_3_t$conf.int[2],2)`], *d* = `r rd(ra_1_3_d$est,2)`

#####Schools 1 and 4 [ra_1_4]  
*t*(`r rd(ra_1_4_t$par,2)`) = `r rd(ra_1_4_t$stat,2)`, *p* `r format_pval(ra_1_4_t$p.value)`, 95% CI [`r rd(ra_1_4_t$conf.int[1],2)`, `r rd(ra_1_4_t$conf.int[2],2)`], *d* = `r rd(ra_1_4_d$est,2)`

#####Schools 4 and 2 [ra_4_2]  
*t*(`r rd(ra_4_2_t$par,2)`) = `r rd(ra_4_2_t$stat,2)`, *p* `r format_pval(ra_4_2_t$p.value)`, 95% CI [`r rd(ra_4_2_t$conf.int[1],2)`, `r rd(ra_4_2_t$conf.int[2],2)`], *d* = `r rd(ra_4_2_d$est,2)`

#####Schools 4 and 2 [ra_4_2]  
*t*(`r rd(ra_4_3_t$par,2)`) = `r rd(ra_4_3_t$stat,2)`, *p* `r format_pval(ra_4_3_t$p.value)`, 95% CI [`r rd(ra_4_3_t$conf.int[1],2)`, `r rd(ra_4_3_t$conf.int[2],2)`], *d* = `r rd(ra_4_3_d$est,2)`






#Self-reported prosocial behavior by school
```{r prosocial behavior by school, include=FALSE}

prosocialSchoolAOV = aov(CSBSprosocial ~ School, data=d0)
summary(prosocialSchoolAOV)
etaSquared(prosocialSchoolAOV)

#comparisons 
bartlett.test(CSBSprosocial~School, data = d0) #can't assume equal variance


#School 1 and 2
pro_1_2_t = t.test(d0$CSBSprosocial[d0$School=="1"],d0$CSBSprosocial[d0$School=="2"],var.equal = FALSE)
pro_1_2_d = cohen.d(d0$CSBSprosocial[d0$School=="1"],d0$CSBSprosocial[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 3
pro_1_3_t = t.test(d0$CSBSprosocial[d0$School=="1"],d0$CSBSprosocial[d0$School=="3"],var.equal = FALSE)
pro_1_3_d = cohen.d(d0$CSBSprosocial[d0$School=="1"],d0$CSBSprosocial[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 4
pro_1_4_t = t.test(d0$CSBSprosocial[d0$School=="1"],d0$CSBSprosocial[d0$School=="4"],var.equal = FALSE)
pro_1_4_d = cohen.d(d0$CSBSprosocial[d0$School=="1"],d0$CSBSprosocial[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 3
pro_2_3_t = t.test(d0$CSBSprosocial[d0$School=="2"],d0$CSBSprosocial[d0$School=="3"],var.equal = FALSE)
pro_2_3_d = cohen.d(d0$CSBSprosocial[d0$School=="2"],d0$CSBSprosocial[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 4
pro_2_4_t = t.test(d0$CSBSprosocial[d0$School=="2"],d0$CSBSprosocial[d0$School=="4"],var.equal = FALSE)
pro_2_4_d = cohen.d(d0$CSBSprosocial[d0$School=="2"],d0$CSBSprosocial[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 3 and 4
pro_3_4_t = t.test(d0$CSBSprosocial[d0$School=="3"],d0$CSBSprosocial[d0$School=="4"],var.equal = FALSE)
pro_3_4_d = cohen.d(d0$CSBSprosocial[d0$School=="3"],d0$CSBSprosocial[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)
```

#####Schools 1 and 3 [pro_1_3]  
*t*(`r rd(pro_1_3_t$par,2)`) = `r rd(pro_1_3_t$stat,2)`, *p* `r format_pval(pro_1_3_t$p.value)`, 95% CI [`r rd(pro_1_3_t$conf.int[1],2)`, `r rd(pro_1_3_t$conf.int[2],2)`], *d* = `r rd(pro_1_3_d$est,2)`

#####Schools 1 and 4 [pro_1_4]  
*t*(`r rd(pro_1_4_t$par,2)`) = `r rd(pro_1_4_t$stat,2)`, *p* `r format_pval(pro_1_4_t$p.value)`, 95% CI [`r rd(pro_1_4_t$conf.int[1],2)`, `r rd(pro_1_4_t$conf.int[2],2)`], *d* = `r rd(pro_1_4_d$est,2)`

#####Schools 2 and 3 [pro_2_3]  
*t*(`r rd(pro_2_3_t$par,2)`) = `r rd(pro_2_3_t$stat,2)`, *p* `r format_pval(pro_2_3_t$p.value)`, 95% CI [`r rd(pro_2_3_t$conf.int[1],2)`, `r rd(pro_2_3_t$conf.int[2],2)`], *d* = `r rd(pro_2_3_d$est,2)`

#####Schools 1 and 2 [pro_1_2]  
*t*(`r rd(pro_1_2_t$par,2)`) = `r rd(pro_1_2_t$stat,2)`, *p* `r format_pval(pro_1_2_t$p.value)`, 95% CI [`r rd(pro_1_2_t$conf.int[1],2)`, `r rd(pro_1_2_t$conf.int[2],2)`], *d* = `r rd(pro_1_2_d$est,2)`

#####Schools 2 and 4 [pro_2_4]  
*t*(`r rd(pro_2_4_t$par,2)`) = `r rd(pro_2_4_t$stat,2)`, *p* `r format_pval(pro_2_4_t$p.value)`, 95% CI [`r rd(pro_2_4_t$conf.int[1],2)`, `r rd(pro_2_4_t$conf.int[2],2)`], *d* = `r rd(pro_2_4_d$est,2)`

#####Schools 3 and 4 [pro_3_4]  
*t*(`r rd(pro_3_4_t$par,2)`) = `r rd(pro_3_4_t$stat,2)`, *p* `r format_pval(pro_3_4_t$p.value)`, 95% CI [`r rd(pro_3_4_t$conf.int[1],2)`, `r rd(pro_3_4_t$conf.int[2],2)`], *d* = `r rd(pro_3_4_d$est,2)`





#Creating Figure 1 (empathic motivation)

```{Make figure 1, include=FALSE}
cbPalette = c("#512857","#4254AE", "#1DA29B") #color palette 

#Empathic Motives
EmpMotives_agg = d0 %>%
  group_by(Group) %>%
  summarise(mean=mean(EmpMotivesComp, na.rm = T), sd=sd(EmpMotivesComp,na.rm=T), n = sum(!is.na(EmpMotivesComp)), se = sd/sqrt(n))

empMotives = ggplot(EmpMotives_agg, aes(x=Group, y=mean, fill = Group)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
scale_fill_manual(values=cbPalette, 
                   name = "Condition",
                   labels = c("Control", "Social Norms", "Malleable"))+ geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 xlab("Group") +
 ylab("Composite Score Total") +
 ggtitle("Empathic Motivation") +
 theme(legend.position="none") +
 scale_x_discrete(labels=c("Control","Norms","Mindset")) +
 scale_y_continuous(limits=c(0,65),breaks=1:65*2) +         # Specifying y scale and points
 theme(plot.title = element_text(hjust = 0.5)) + 
coord_cartesian(ylim=c(34,42)) 


ggsave("~/Dropbox/middleSchoolManuscript/Current/Fig1.jpg", width = 3.5, height = 3,dpi = 300)
```



#Creating Figure 2 (Engagement scores by school)
```{r Making figure 2, include=FALSE}
engageSelf_School = d0 %>%
  group_by(School) %>%
  summarise(mean=mean(carefulYouSesAvg, na.rm = T), sd=sd(carefulYouSesAvg,na.rm=T), n = sum(!is.na(carefulYouSesAvg)), se = sd/sqrt(n))

engageSelf_plot = ggplot(engageSelf_School,
         aes(x=School, y=mean, fill = School)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Self-Reported \nIntervention Engagement") +
 scale_y_continuous(limits=c(0,5),breaks=0:25*.2) +        
 theme(plot.title = element_text(hjust = 0.5)) +
 ylab("Composite Self-Reported \nEngagement Score") +
 coord_cartesian(ylim=c(2.75,4)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none") 

engagePeers_School = d0 %>%
  group_by(School) %>%
  summarise(mean=mean(carefulPeersSesAvg, na.rm = T), sd=sd(carefulPeersSesAvg,na.rm=T), n = sum(!is.na(carefulPeersSesAvg)), se = sd/sqrt(n))

engagePeers_plot = ggplot(engagePeers_School,
         aes(x=School, y=mean, fill = School)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Perceptions of Peer \nIntervention Engagement") +
 scale_y_continuous(limits=c(0,5),breaks=0:25*.3) +        
 theme(plot.title = element_text(hjust = 0.5)) +
 ylab("Composite Peer \nEngagement Score") +
 coord_cartesian(ylim=c(3.,4.6)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none") 
 
ggarrange(engageSelf_plot, engagePeers_plot, labels = c("A)","B)"), ncol = 2)
ggsave("~/Dropbox/middleSchoolManuscript/Current/Fig2.jpg", width = 6.5, height = 3, dpi = 300)
```



#Creating figure 3, physical and relational aggression by school
```{r Making figure 3, include=FALSE}
phys_School = d0 %>%
  group_by(School) %>%
  summarise(mean=mean(CSBSphys, na.rm = T), sd=sd(CSBSphys,na.rm=T), n = sum(!is.na(CSBSphys)), se = sd/sqrt(n))

phys_Plot = ggplot(phys_School,
         aes(x=School, y=mean, fill = School)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Self-Reported \nPhysical Aggression") +
 scale_y_continuous(limits=c(0,10),breaks=0:25*.5) +        
 theme(plot.title = element_text(hjust = 0.5)) +
 ylab("Subscale Score") +
 coord_cartesian(ylim=c(2.5, 4)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none") 



realt_School = d0 %>%
  group_by(School) %>%
  summarise(mean=mean(CSBSrelat, na.rm = T), sd=sd(CSBSrelat,na.rm=T), n = sum(!is.na(CSBSrelat)), se = sd/sqrt(n))

relat_Plot = ggplot(realt_School,
         aes(x=School, y=mean, fill = School)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Self-Reported \nRelational Aggression") +
 scale_y_continuous(limits=c(0,10),breaks=0:25*.5) +        
 theme(plot.title = element_text(hjust = 0.5)) +
 ylab("Subscale Score") +
 coord_cartesian(ylim=c(7, 10)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none") 

ggarrange(phys_Plot, relat_Plot, labels = c("A)","B)"), ncol = 2)
ggsave("~/Dropbox/middleSchoolManuscript/Current/Fig3.jpg", width = 6.5, height = 3, dpi = 300)
```

#Creating Figure 4 (Empathic motives and normativity beliefs by school and group)
```{r Making figure 4, include=FALSE}
cbPalette = c("#512857","#4254AE", "#1DA29B") #color palette 

Empathic_Motives_School_Group = d0 %>%
  group_by(Group,School) %>%
  summarise(mean=mean(EmpMotivesComp, na.rm = T), sd=sd(EmpMotivesComp,na.rm=T), n = sum(!is.na(EmpMotivesComp)), se = sd/sqrt(n))

motivesPlot = ggplot(Empathic_Motives_School_Group,
         aes(x=School, y=mean, fill = Group)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 scale_fill_manual(values=cbPalette, 
                   name = "Condition",
                   labels = c("Control", "Malleable","Social Norms"))+
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Empathic Motives") +
 scale_y_continuous(limits=c(0,65),breaks=1:65*2) +         # Specifying y scale and points
 #theme_bw(base_size = 16) +
 theme(plot.title = element_text(hjust = 0.5))  +
 ylab("Motives Scale Score") + 
 coord_cartesian(ylim=c(34,44)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none")


Normativity_School_Group = d0 %>%
  group_by(Group,School) %>%
  summarise(mean=mean(NormsTotal, na.rm = T), sd=sd(NormsTotal,na.rm=T), n = sum(!is.na(NormsTotal)), se = sd/sqrt(n))


normsPlot = ggplot(Normativity_School_Group, aes(x=School, y=mean, fill = Group)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 scale_fill_manual(values=cbPalette, 
                   name = "Condition",
                   labels = c("Control", "Malleable","Social Norms"))+
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Normativity Beliefs") +
 scale_y_continuous(limits=c(0,35),breaks=1:63*2) +        
 theme(plot.title = element_text(hjust = 0.5)) +
 ylab("Normativity Scale Score") +
 coord_cartesian(ylim=c(24,32)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none") 

ggarrange(motivesPlot, normsPlot, labels = c("A)","B)"), ncol = 2)
ggsave("~/Dropbox/middleSchoolManuscript/Current/Fig4.jpg", width = 6.5, height = 3, dpi = 300)
```


#SUPPLEMENT: Skepticism about empathy
```{r supplement skepticism about empathy for , include=FALSE}
empNotGoodSchoolAOV = aov(empNotGood ~ School, data=d0)
summary(empNotGoodSchoolAOV)
etaSquared(empNotGoodSchoolAOV)


#comparisons 
bartlett.test(empNotGood~School, data = d0) #can't assume equal variance


#School 1 and 2
t.test(d0$empNotGood[d0$School=="1"],d0$empNotGood[d0$School=="2"],var.equal = FALSE)
cohen.d(d0$empNotGood[d0$School=="1"],d0$empNotGood[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 3
t.test(d0$empNotGood[d0$School=="1"],d0$empNotGood[d0$School=="3"],var.equal = FALSE)
cohen.d(d0$empNotGood[d0$School=="1"],d0$empNotGood[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 1 and 4
t.test(d0$empNotGood[d0$School=="1"],d0$empNotGood[d0$School=="4"],var.equal = FALSE)
cohen.d(d0$empNotGood[d0$School=="1"],d0$empNotGood[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#School 2 and 3
t.test(d0$empNotGood[d0$School=="2"],d0$empNotGood[d0$School=="3"],var.equal = FALSE)
cohen.d(d0$empNotGood[d0$School=="2"],d0$empNotGood[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#School 3 and 4
t.test(d0$empNotGood[d0$School=="3"],d0$empNotGood[d0$School=="4"],var.equal = FALSE)
cohen.d(d0$empNotGood[d0$School=="3"],d0$empNotGood[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

empNotGood_School = d0 %>%
  group_by(School) %>%
  summarise(mean=mean(empNotGood, na.rm = T), sd=sd(empNotGood,na.rm=T), n = sum(!is.na(empNotGood)), se = sd/sqrt(n))

empNotGood_School_plot = ggplot(empNotGood_School,
         aes(x=School, y=mean, fill = School)) + #bar graph
 geom_bar(position=position_dodge(), stat="identity",
          colour="black", # Use black outlines,
          size=.3) +
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
               colour="black",
               size=.4,
               width=.2,                    # Width of the error bars
               position=position_dodge(.9)) +
 ggtitle("Skepticism about \nEmpathy") +
 scale_y_continuous(limits=c(0,5),breaks=0:25*.3) +        
 theme(plot.title = element_text(hjust = 0.5)) +
 ylab("Question Score") +
 coord_cartesian(ylim=c(2,3.8)) +
 theme(axis.title.x=element_blank()) +
 scale_x_discrete(labels=c("School \n 1","School \n 2","School \n 3","School \n 4")) +
 theme(legend.position="none") 


#Missing data tables for supplement
addmargins(table(d0$Group[which(is.na(d0$EmpMotivesComp))])) #Empathic motives
addmargins(table(d0$Group[which(is.na(d0$CSBSrelat))])) #Relational aggression
addmargins(table(d0$Group[which(is.na(d0$CSBSpro))])) #Self-reported prosocial behavior
addmargins(table(d0$Group[which(is.na(d0$CSBSphys))])) #Physical aggression
addmargins(table(d0$Group[which(is.na(d0$ECtotal))])) #IRI empathic concern
addmargins(table(d0$Group[which(is.na(d0$PDtotal))])) #IRI personal distress
addmargins(table(d0$Group[which(is.na(d0$PTtotal))])) #IRI perspective taking
addmargins(table(d0$Group[which(is.na(d0$LonelyTotal))])) #Loneliness
addmargins(table(d0$Group[which(is.na(d0$PSSTotal))])) #Stress
addmargins(table(d0$Group[which(is.na(d0$MalTotal))])) #Malleability beliefs
addmargins(table(d0$Group[which(is.na(d0$NormsTotal))])) #Norms beliefs
```

#SUPPLEMENT: SNI vs MMI and CI

```{r coding for SNI vs other two conditions, supplemental analysis}
d0$normsIntervention = NA
d0$normsIntervention[d0$Group == c("SNI")] = 1
d0$normsIntervention[d0$Group == c("MMI")] = 0
d0$normsIntervention[d0$Group == c("CI")] = 0

d3 = subset(d0,School != 1) 

x = d3$normsIntervention
y = d3$prosocialNomsTotal
m = d3$EmpMotivesComp

DataProNoms_SNI_v_MMI_CI <- data.frame(X = x, Y = y, M = m)

model_simplemed <-  '# direct effect
                     Y ~ c*X
                     # mediator
                     M ~ a*X
                     Y ~ b*M
                     # indirect effect (a*b)
                     ab := a*b
                     # total effect
                     total := c + (a*b)
                     '
         
fit <- sem(model_simplemed, data = DataProNoms_SNI_v_MMI_CI)
summary(fit)


set.seed(1234)

#for boot strapped 95% CIs
fit <- sem(model_simplemed, data=DataProNoms_SNI_v_MMI_CI, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)

boot.fit <- parameterEstimates(fit)
boot.fit
```

#SUPPLEMENT: Indirect effect with all four schools

```{r including all four schools in SEM, supplemental analysis}
d0_SNI_CI = subset(d0,Group != "MMI") #remove malleable so as to compare social norms to control condition
d0_SNI_CI$Group <- factor(d0_SNI_CI$Group, levels = c("CI","SNI")) 
contrasts(d0_SNI_CI$Group)

x = d0_SNI_CI$Group
y = d0_SNI_CI$prosocialNomsTotal
m = d0_SNI_CI$EmpMotivesComp

DataProNoms_all <- data.frame(X = x, Y = y, M = m)

model_simplemed <-  '# direct effect
                     Y ~ c*X
                     # mediator
                     M ~ a*X
                     Y ~ b*M
                     # indirect effect (a*b)
                     ab := a*b
                     # total effect
                     total := c + (a*b)
                     '
         
fit <- sem(model_simplemed, data = DataProNoms_all)
summary(fit)

#for boot strapped 95% CIs
fit <- sem(model_simplemed, data=DataProNoms_SNI_v_MMI_CI, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)

boot.fit <- parameterEstimates(fit)
boot.fit
```