---
title: Empathy Middle School Analyses with Pilot
author: Erika Weisz
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r set wd and read data, include=FALSE}
#Set working directory to the location of this .Rmd file (note: the dataset should be in the same folder)
  setwd("~/Dropbox/middleSchoolManuscript/Current")
  d0 = read.csv('empathyMiddleSchool_withPilot.csv')
```

```{r install packages, include=FALSE}
#install packages
library("knitr") 
library("plyr")
library("dplyr")
library("ggplot2")
library("gridExtra")
library("grid")
library("lattice")
library("psych")
library("lsr")
library("effsize")
library("weights")
library("ggpubr")
library("lavaan")
```

```{r knit functions, echo=FALSE}
#formatting p-values for APA
format_pval <- function(x){
  if (x < .001) return(paste('<', '.001'))
  if (x > .1) return(paste('=', rd(x, 2)))
  paste('=', rd(x, 3))   # 3 = no. of digits to round p value to if p < .001 
}
##########################################
```

```{r changing levels for figure, include=FALSE}
levels(d0$Group) 
#default is Control, Malleable, Social Norms

d0$Group <- factor(d0$Group, levels = c("CI","SNI","MMI"))
#Levels now set to Control, Social Norms, Malleable Mindset for figure
#CI = Control
#MMI = Malleable Mindset
#SNI = Social Norms
```

```{r setting school as a factor, include=FALSE}
d0$School = as.factor(d0$School) #make sure it's not is numeric
```


#Normativity Beliefs
```{r normativity beliefs, include=FALSE}
#assessing scores on beliefs about the normativity of empathy questionnaire at follow up
normativityAOV = aov(NormsTotal ~ Group, data=d0)
summary(normativityAOV)
etaSquared(normativityAOV)

#comparisons 
bartlett.test(NormsTotal~Group, data = d0) #don't assume equal variance

#Social Norms and Control
nb_SNI_CI_t = t.test(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="CI"],var.equal = FALSE)
nb_SNI_CI_d = cohen.d(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)

#Social Norms and Malleable Mindset
nb_SNI_MMI_t = t.test(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="MMI"],var.equal = FALSE)
nb_SNI_MMI_d = cohen.d(d0$NormsTotal[d0$Group=="SNI"],d0$NormsTotal[d0$Group=="MMI"],return.dm=TRUE, na.rm=TRUE)

#Malleable Mindset and Control
nb_MMI_CI_t = t.test(d0$NormsTotal[d0$Group=="MMI"],d0$NormsTotal[d0$Group=="CI"],var.equal = FALSE)
nb_MMI_CI_d = cohen.d(d0$NormsTotal[d0$Group=="MMI"],d0$NormsTotal[d0$Group=="CI"],return.dm=TRUE, na.rm=TRUE)


```
(Ordered by appearance in manuscript)

#####Social Norms and Control [nb_SNI_CI]  
*t*(`r rd(nb_SNI_CI_t$par,2)`) = `r rd(nb_SNI_CI_t$stat,2)`, *p* `r format_pval(nb_SNI_CI_t$p.value)`, 95% CI [`r rd(nb_SNI_CI_t$conf.int[1],2)`, `r rd(nb_SNI_CI_t$conf.int[2],2)`], *d* = `r rd(nb_SNI_CI_d$est,2)`

#####Social Norms and Malleable Mindset [nb_SNI_MMI]  
*t*(`r rd(nb_SNI_MMI_t$par,2)`) = `r rd(nb_SNI_MMI_t$stat,2)`, *p* `r format_pval(nb_SNI_MMI_t$p.value)`, 95% CI [`r rd(nb_SNI_MMI_t$conf.int[1],2)`, `r rd(nb_SNI_MMI_t$conf.int[2],2)`], *d* = `r rd(nb_SNI_MMI_d$est,2)`

#####Malleable Mindset and Control [nb_MMI_CI]  
*t*(`r rd(nb_MMI_CI_t$par,2)`) = `r rd(nb_MMI_CI_t$stat,2)`, *p* `r format_pval(nb_MMI_CI_t$p.value)`, 95% CI [`r rd(nb_MMI_CI_t$conf.int[1],2)`, `r rd(nb_MMI_CI_t$conf.int[2],2)`], *d* = `r rd(nb_MMI_CI_d$est,2)`



#Malleability Beliefs
```{r malleability beliefs, include=FALSE}
#assessing scores on beliefs about the malleability of empathy questionnaire at follow up
malleabilityAOV = aov(MalTotal ~ Group, data=d0)
summary(malleabilityAOV)
etaSquared(malleabilityAOV)
```


#Physical Aggression
```{r physical aggression, include=FALSE}
#Comparing scores on self-reported physical aggression

physAOV = aov(CSBSphys ~ Group, data=d0)
summary(physAOV)
etaSquared(physAOV)
```

#Relational Aggression
```{r relational aggression, include=FALSE}
#Comparing scores on self-reported relational aggression

raggAOV = aov(CSBSrelat ~ Group, data=d0)
summary(raggAOV)
etaSquared(raggAOV)
```

#Stress
```{r stress, include=FALSE}
#Comparing scores on self-reported stress

stressAOV = aov(PSSTotal ~ Group, data=d0)
summary(stressAOV)
etaSquared(stressAOV)
```

#Loneliness
```{r loneliness, include=FALSE}
#Comparing scores on self-reported loneliness

lonelyAOV = aov(LonelyTotal ~ Group, data=d0)
summary(lonelyAOV)
etaSquared(lonelyAOV)
```

#Empathic Concern
```{r empathic concern, include=FALSE}
#Comparing scores on self-reported empathic concern

ecAOV = aov(ECtotal ~ Group, data=d0)
summary(ecAOV)
etaSquared(ecAOV)
```

#Perspective Taking
```{r perspective taking, include=FALSE}
#Comparing scores on self-reported perspective taking

ptAOV = aov(PTtotal ~ Group, data=d0)
summary(ptAOV)
etaSquared(ptAOV)
```

#Personal Distress
```{r personal distress, include=FALSE}
#Comparing scores on self-reported personal distress

pdAOV = aov(PDtotal ~ Group, data=d0)
summary(pdAOV)
etaSquared(pdAOV)
```

#Peer-reported prosocial behavior
```{r peer reported prosocial beahvior, include=FALSE}
proNomsAOV = aov(prosocialNomsTotal ~ Group, data=d0)
summary(proNomsAOV)
etaSquared(proNomsAOV)
```

#CSBS Prosocial
```{r self-reported prosocial behavior, include=FALSE}
#Comparing scores on self-reported prosocial behavior

selfProAOV = aov(CSBSprosocial ~ Group, data=d0)
summary(selfProAOV)
etaSquared(selfProAOV)
```

#Intervention Engagement, self
```{r intervention engagement self, include=FALSE}
#assessing self-reported engagement during three intervention sessions
engageSelfAOV = aov(carefulYouSesAvg ~ Group, data=d0)
summary(engageSelfAOV)
etaSquared(engageSelfAOV)
```

#Intervention Engagement, peers
```{r intervention engagement peers, include=FALSE}
#assessing perceptions of peer engagement during three intervention sessions
engagePeersAOV = aov(carefulPeersSesAvg ~ Group, data=d0)
summary(engagePeersAOV)
etaSquared(engagePeersAOV)
```

#Intervention Engagement, self by school
```{r intervention engagement self by school, include=FALSE}
#assessing self-reported engagement during three intervention sessions (looking across schools)
engageSelfSchoolAOV = aov(carefulYouSesAvg ~ School, data=d0)
summary(engageSelfSchoolAOV)
etaSquared(engageSelfSchoolAOV)

#comparisons 
bartlett.test(carefulYouSesAvg~School, data = d0) #assume equal variance

#1 and 2
se_1_2_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = TRUE)
se_1_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#1 and 3
se_1_3_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="3"],var.equal = TRUE)
se_1_3_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#1 and 4
se_1_4_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
se_1_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#1 and pilot
se_1_pilot_t = t.test(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="pilot"],var.equal = TRUE)
se_1_pilot_d = cohen.d(d0$carefulYouSesAvg[d0$School=="1"],d0$carefulYouSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#3 and 2
se_3_2_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = TRUE)
se_3_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#3 and 4
se_3_4_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
se_3_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#3 and pilot
se_3_pilot_t = t.test(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="pilot"],var.equal = TRUE)
se_3_pilot_d = cohen.d(d0$carefulYouSesAvg[d0$School=="3"],d0$carefulYouSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#pilot and 2
se_pilot_2_t = t.test(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="2"],var.equal = TRUE)
se_pilot_2_d = cohen.d(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#pilot and 4
se_pilot_4_t = t.test(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
se_pilot_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="pilot"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#2 and 4
se_2_4_t = t.test(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="4"],var.equal = TRUE)
se_2_4_d = cohen.d(d0$carefulYouSesAvg[d0$School=="2"],d0$carefulYouSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

```
(Ordered by appearance in manuscript)

#####1 and 2 [se_1_2]  
*t*(`r rd(se_1_2_t$par,2)`) = `r rd(se_1_2_t$stat,2)`, *p* `r format_pval(se_1_2_t$p.value)`, 95% CI [`r rd(se_1_2_t$conf.int[1],2)`, `r rd(se_1_2_t$conf.int[2],2)`], *d* = `r rd(se_1_2_d$est,2)`

#####1 and 3 [se_1_3]  
*t*(`r rd(se_1_3_t$par,2)`) = `r rd(se_1_3_t$stat,2)`, *p* `r format_pval(se_1_3_t$p.value)`, 95% CI [`r rd(se_1_3_t$conf.int[1],2)`, `r rd(se_1_3_t$conf.int[2],2)`], *d* = `r rd(se_1_3_d$est,2)`

#####1 and 4 [se_1_4]  
*t*(`r rd(se_1_4_t$par,2)`) = `r rd(se_1_4_t$stat,2)`, *p* `r format_pval(se_1_4_t$p.value)`, 95% CI [`r rd(se_1_4_t$conf.int[1],2)`, `r rd(se_1_4_t$conf.int[2],2)`], *d* = `r rd(se_1_4_d$est,2)`

#####1 and pilot [se_1_pilot]  
*t*(`r rd(se_1_pilot_t$par,2)`) = `r rd(se_1_pilot_t$stat,2)`, *p* `r format_pval(se_1_pilot_t$p.value)`, 95% CI [`r rd(se_1_pilot_t$conf.int[1],2)`, `r rd(se_1_pilot_t$conf.int[2],2)`], *d* = `r rd(se_1_pilot_d$est,2)`

#####3 and 2 [se_3_2]  
*t*(`r rd(se_3_2_t$par,2)`) = `r rd(se_3_2_t$stat,2)`, *p* `r format_pval(se_3_2_t$p.value)`, 95% CI [`r rd(se_3_2_t$conf.int[1],2)`, `r rd(se_3_2_t$conf.int[2],2)`], *d* = `r rd(se_3_2_d$est,2)`

#####3 and 4 [se_3_4]  
*t*(`r rd(se_3_4_t$par,2)`) = `r rd(se_3_4_t$stat,2)`, *p* `r format_pval(se_3_4_t$p.value)`, 95% CI [`r rd(se_3_4_t$conf.int[1],2)`, `r rd(se_3_4_t$conf.int[2],2)`], *d* = `r rd(se_3_4_d$est,2)`


#####3 and pilot [se_3_pilot]  
*t*(`r rd(se_3_pilot_t$par,2)`) = `r rd(se_3_pilot_t$stat,2)`, *p* `r format_pval(se_3_pilot_t$p.value)`, 95% CI [`r rd(se_3_pilot_t$conf.int[1],2)`, `r rd(se_3_pilot_t$conf.int[2],2)`], *d* = `r rd(se_3_pilot_d$est,2)`

#####pilot and 2 [se_pilot_2]  
*t*(`r rd(se_pilot_2_t$par,2)`) = `r rd(se_pilot_2_t$stat,2)`, *p* `r format_pval(se_pilot_2_t$p.value)`, 95% CI [`r rd(se_pilot_2_t$conf.int[1],2)`, `r rd(se_pilot_2_t$conf.int[2],2)`], *d* = `r rd(se_pilot_2_d$est,2)`

#####pilot and 4 [se_pilot_4]  
*t*(`r rd(se_pilot_4_t$par,2)`) = `r rd(se_pilot_4_t$stat,2)`, *p* `r format_pval(se_pilot_4_t$p.value)`, 95% CI [`r rd(se_pilot_4_t$conf.int[1],2)`, `r rd(se_pilot_4_t$conf.int[2],2)`], *d* = `r rd(se_pilot_4_d$est,2)`

#####2 and 4 [se_2_4]  
*t*(`r rd(se_2_4_t$par,2)`) = `r rd(se_2_4_t$stat,2)`, *p* `r format_pval(se_2_4_t$p.value)`, 95% CI [`r rd(se_2_4_t$conf.int[1],2)`, `r rd(se_2_4_t$conf.int[2],2)`], *d* = `r rd(se_2_4_d$est,2)`

#Intervention Engagement, peers by school
```{r intervention engagement peers by school, include=FALSE}
#assessing perceptions of peer engagement during three intervention sessions (looking across schools)
engagePeersSchoolAOV = aov(carefulPeersSesAvg ~ School, data=d0)
summary(engagePeersSchoolAOV)
etaSquared(engagePeersSchoolAOV)

#comparisons 
bartlett.test(carefulPeersSesAvg~School, data = d0) #can't assume equal variance


#1 and 2
pe_1_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = TRUE)
pe_1_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#1 and 3
pe_1_3_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="3"],var.equal = TRUE)
pe_1_3_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="3"],return.dm=TRUE, na.rm=TRUE)

#1 and 4
pe_1_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
pe_1_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#1 and pilot
pe_1_pilot_t = t.test(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="pilot"],var.equal = TRUE)
pe_1_pilot_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="1"],d0$carefulPeersSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#3 and 2
pe_3_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = TRUE)
pe_3_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#3 and 4
pe_3_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
pe_3_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#3 and pilot
pe_3_pilot_t = t.test(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="pilot"],var.equal = TRUE)
pe_3_pilot_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="3"],d0$carefulPeersSesAvg[d0$School=="pilot"],return.dm=TRUE, na.rm=TRUE)

#pilot and 2
pe_pilot_2_t = t.test(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="2"],var.equal = TRUE)
pe_pilot_2_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="2"],return.dm=TRUE, na.rm=TRUE)

#pilot and 4
pe_pilot_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
pe_pilot_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="pilot"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

#2 and 4
pe_2_4_t = t.test(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="4"],var.equal = TRUE)
pe_2_4_d = cohen.d(d0$carefulPeersSesAvg[d0$School=="2"],d0$carefulPeersSesAvg[d0$School=="4"],return.dm=TRUE, na.rm=TRUE)

```
(Ordered by appearance in manuscript)

#####1 and 2 [pe_1_2]  
*t*(`r rd(pe_1_2_t$par,2)`) = `r rd(pe_1_2_t$stat,2)`, *p* `r format_pval(pe_1_2_t$p.value)`, 95% CI [`r rd(pe_1_2_t$conf.int[1],2)`, `r rd(pe_1_2_t$conf.int[2],2)`], *d* = `r rd(pe_1_2_d$est,2)`

#####1 and 3 [pe_1_3]  
*t*(`r rd(pe_1_3_t$par,2)`) = `r rd(pe_1_3_t$stat,2)`, *p* `r format_pval(pe_1_3_t$p.value)`, 95% CI [`r rd(pe_1_3_t$conf.int[1],2)`, `r rd(pe_1_3_t$conf.int[2],2)`], *d* = `r rd(pe_1_3_d$est,2)`

#####1 and 4 [pe_1_4]  
*t*(`r rd(pe_1_4_t$par,2)`) = `r rd(pe_1_4_t$stat,2)`, *p* `r format_pval(pe_1_4_t$p.value)`, 95% CI [`r rd(pe_1_4_t$conf.int[1],2)`, `r rd(pe_1_4_t$conf.int[2],2)`], *d* = `r rd(pe_1_4_d$est,2)`

#####1 and pilot [pe_1_pilot]  
*t*(`r rd(pe_1_pilot_t$par,2)`) = `r rd(pe_1_pilot_t$stat,2)`, *p* `r format_pval(pe_1_pilot_t$p.value)`, 95% CI [`r rd(pe_1_pilot_t$conf.int[1],2)`, `r rd(pe_1_pilot_t$conf.int[2],2)`], *d* = `r rd(pe_1_pilot_d$est,2)`

#####3 and 2 [pe_3_2]  
*t*(`r rd(pe_3_2_t$par,2)`) = `r rd(pe_3_2_t$stat,2)`, *p* `r format_pval(pe_3_2_t$p.value)`, 95% CI [`r rd(pe_3_2_t$conf.int[1],2)`, `r rd(pe_3_2_t$conf.int[2],2)`], *d* = `r rd(pe_3_2_d$est,2)`

#####3 and 4 [pe_3_4]  
*t*(`r rd(pe_3_4_t$par,2)`) = `r rd(pe_3_4_t$stat,2)`, *p* `r format_pval(pe_3_4_t$p.value)`, 95% CI [`r rd(pe_3_4_t$conf.int[1],2)`, `r rd(pe_3_4_t$conf.int[2],2)`], *d* = `r rd(pe_3_4_d$est,2)`


#####3 and pilot [pe_3_pilot]  
*t*(`r rd(pe_3_pilot_t$par,2)`) = `r rd(pe_3_pilot_t$stat,2)`, *p* `r format_pval(pe_3_pilot_t$p.value)`, 95% CI [`r rd(pe_3_pilot_t$conf.int[1],2)`, `r rd(pe_3_pilot_t$conf.int[2],2)`], *d* = `r rd(pe_3_pilot_d$est,2)`

#####pilot and 2 [pe_pilot_2]  
*t*(`r rd(pe_pilot_2_t$par,2)`) = `r rd(pe_pilot_2_t$stat,2)`, *p* `r format_pval(pe_pilot_2_t$p.value)`, 95% CI [`r rd(pe_pilot_2_t$conf.int[1],2)`, `r rd(pe_pilot_2_t$conf.int[2],2)`], *d* = `r rd(pe_pilot_2_d$est,2)`

#####pilot and 4 [pe_pilot_4]  
*t*(`r rd(pe_pilot_4_t$par,2)`) = `r rd(pe_pilot_4_t$stat,2)`, *p* `r format_pval(pe_pilot_4_t$p.value)`, 95% CI [`r rd(pe_pilot_4_t$conf.int[1],2)`, `r rd(pe_pilot_4_t$conf.int[2],2)`], *d* = `r rd(pe_pilot_4_d$est,2)`

#####2 and 4 [pe_2_4]  
*t*(`r rd(pe_2_4_t$par,2)`) = `r rd(pe_2_4_t$stat,2)`, *p* `r format_pval(pe_2_4_t$p.value)`, 95% CI [`r rd(pe_2_4_t$conf.int[1],2)`, `r rd(pe_2_4_t$conf.int[2],2)`], *d* = `r rd(pe_2_4_d$est,2)`




